Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-10-02 packages/spec-haskell/yellowpaper/Paper1.tex
cleanup chapter 2

>>>>

\subsubsection{Haskell Code Conventions Used}

Before first time in this paper listing specification in Haskell, here are some highlights of
conventions in the style of the code used.

The specification is written in Haskell with \textit{GHC2021 language set}\footnote{The complete set
of the extensions is enumerated in
\url{https://downloads.haskell.org/ghc/latest/docs/users_guide/exts/control.html\#extension-GHC2021}.}.

\paragraph{Indexed Types and Type Equality}

In order to make the specification free of specific choices of core data types in
implementation, \textit{FunctionalDependencies}, \textit{TypeFamilies}
and \textit{TypeFamilyDependencies} are extensively used. And in order to make the code less
cluttered, type quality operator $(\sim)$
used. Here is an example:

\begin{code}
    type (~) :: forall k. k -> k -> Constraint

    monetaryValue :: ( mv  ~ MD_MVAL md
                     , mu  ~ MD_MU md
                     , ctx ~ MD_CTX md
                     )
                  => md -> (mu, ctx) -> mv
\end{code}

The otherwise tedious type family synonyms ``\mintinline{haskell}{MD_XYZ md}'' are rewritten with $mv$
$mu$ $ctx$ with the help of $(\sim)$ operator.
